Supporting Information : The importance of a complete description of dependence between variables for ecology and related fields

### 2019-05-03 SupportingInformation.Rmd
rds to csv storage

<!--reading data and generaing plot for soilCN-->
```{r load_and_plot_data_soilCN, echo=F, results='hide'}
#fig.cap="Plot of the raw soil C and N data.\\label{fig_raw_cop_soilCN}(A)", fig.height=3, fig.width=3}
d<-readRDS("Data/dataForShymolinaCoord.rds")
d<-d[,c("SOCstock100","TSNstock100","lat","long")]
d<-na.omit(d)
pdf("./Results/SoilCNraw.pdf")
op<-par(mar=c(6, 6, 0.2, 2.1))
d_log<-log10(d[,c(1:2)])
plot(d_log[,1],d_log[,2],type="p",col="black",xlab="log(Soil C)",ylab="log(Soil N)",cex.lab=2.5,cex.axis=2.5)
par(op)
dev.off()
```

@@

<!--reading multivariate methane flux data-->
```{r read_methane_data, echo=F, results="markup"}
set.seed(seed)
methane_raw<-readRDS("./Data/Methane_data/methane_data_for_Shyamolina.rds")
```

@@

<!--Load and format the data : methane flux-->
```{r read_format_methane_data, echo=F}

methane_raw<-readRDS("./Data/Methane_data/methane_data_for_Shyamolina.rds")

@@

<!--Do the main computations for nonparametric analysis of methane flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

latlon<-readRDS("./Data/Methane_data/chamberLocations.rds")
chamber_name<-colnames(methane_raw[,c(2:dim(methane_raw)[2])])
ndim<-length(chamber_name)

@@

<!--Following chunk examine the consequence of non-Normal copula atructure on skewness using methane flux data-->
```{r skewness_methane_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

>>>>

<!--reading data and generaing plot for soilCN-->
```{r load_and_plot_data_soilCN, echo=F, results='hide'}
#d_old<-readRDS("Data/dataForShymolinaCoord.rds")
#write.csv(d_old,"./Data/SoilCN/SoilCNdata.csv")
d<-read.csv("./Data/SoilCN/SoilCNdata.csv")
rownames(d)<-d$X
d<-d[,-1]
#sapply(dCN,class)

d<-d[,c("SOCstock100","TSNstock100","lat","long")]
#identical(d_old[,c("SOCstock100","TSNstock100","lat","long")],d) # checked : they are identical :)
d<-na.omit(d)
pdf("./Results/SoilCNraw.pdf")
op<-par(mar=c(6, 6, 0.2, 2.1))
d_log<-log10(d[,c(1:2)])
plot(d_log[,1],d_log[,2],type="p",col="black",xlab="log(Soil C)",ylab="log(Soil N)",cex.lab=2.5,cex.axis=2.5)
par(op)
dev.off()
```

@@

@@

<!--Load and format the data : methane flux-->
```{r read_format_methane_data, echo=F}
#latlon_methane_old<-readRDS("./Data/Methane_data/chamberLocations.rds")
#write.csv(latlon_methane_old,"./Data/Methane_data/chamberLocations.csv",row.names = F)
latlon_methane<-read.csv("./Data/Methane_data/chamberLocations.csv")
#identical(latlon_methane_old,latlon_methane)  # checked : they are identical :)

#methane_raw_old<-readRDS("./Data/Methane_data/methane_data_for_Shyamolina.rds")
#write.csv(methane_raw_old,"./Data/Methane_data/methane_data.csv",row.names = F)
methane_raw<-read.csv("./Data/Methane_data/methane_data.csv")
methane_raw$dates<-as.Date(methane_raw$dates) # converting factor class to date class
#identical(methane_raw_old,methane_raw)  # checked : they are identical :)

@@

<!--Do the main computations for nonparametric analysis of methane flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,methane_raw,latlon_methane,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

latlon<-latlon_methane
chamber_name<-colnames(methane_raw[,c(2:dim(methane_raw)[2])])
ndim<-length(chamber_name)

@@

<!--Following chunk examine the consequence of non-Normal copula atructure on skewness using methane flux data-->
```{r skewness_methane_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}
